Cradles of the first stars: self-shielding, halo masses, and multiplicity

### 2020-01-10 paper.tex
Fixing Schauer units in Figure 10

\begin{figure}
	\includegraphics[width=\columnwidth]{images/compare_JLW_mass.pdf}
    \caption{The halo mass versus the average LW intensity normalized by J21 versus for this work and a variety of other works. The black solid line is from M01 given our LW background, blue solid line from \citet{Trenti09_SFR} at $z=20$, the purple solid line from \citet{Visbal14} at $z=20$, blue open circle from \citet{Yoshida03}, green open squares from \citet{OShea08}, and red open triangles from \citet{Wise07_UVB}. $J_{LW}$ = 0 for the various sources is plotted here at $J_{\rm LW}$/$J_{21}$ = 10$^{-4}$. The right panel represents halo masses corresponding to different streaming velocities from \citet{Naoz13} and \citet{Schauer19}. The solid bands of halo masses correspond to the characteristic masses of haloes to contain a baryon fraction that is half of the cosmic mean for various redshifts and for the shown streaming velocities from \citet{Naoz13}. For each band, the maximum halo mass occurs at $z = 15$. For streaming velocities of $3.4 \sigma_{\rm vbc}$, $1.7 \sigma_{\rm vbc}$, and $1 \sigma_{\rm vbc}$ (5.8 \kms{} at $z=199$), the minimum halo mass occurs at $z = 17, 22, \rm{and} \ 27$, respectively. The minimum halo mass hosting cold dense gas for different streaming velocities, given at their starting redshift $z=199$, from \citet{Schauer19} are shown as horizontal black lines.}
    \label{fig:compare_JLW_mass}
\end{figure}

>>>>

\begin{figure}
	\includegraphics[width=\columnwidth]{images/compare_JLW_mass.pdf}
    \caption{The halo mass versus the average LW intensity normalized by J21 versus for this work and a variety of other works. The black solid line is from M01 given our LW background, blue solid line from \citet{Trenti09_SFR} at $z=20$, the purple solid line from \citet{Visbal14} at $z=20$, blue open circle from \citet{Yoshida03}, green open squares from \citet{OShea08}, and red open triangles from \citet{Wise07_UVB}. $J_{LW}$ = 0 for the various sources is plotted here at $J_{\rm LW}$/$J_{21}$ = 10$^{-4}$. The right panel represents halo masses corresponding to different streaming velocities from \citet{Naoz13} and \citet{Schauer19}. The solid bands of halo masses correspond to the characteristic masses of haloes to contain a baryon fraction that is half of the cosmic mean for various redshifts and for the shown streaming velocities from \citet{Naoz13}. For each band, the maximum halo mass occurs at $z = 15$. For streaming velocities of $3.4 \sigma_{\rm vbc}$, $1.7 \sigma_{\rm vbc}$, and $1 \sigma_{\rm vbc}$ (5.8 \kms{} at $z=199$), the minimum halo mass occurs at $z = 17, 22, \rm{and} \ 27$, respectively. The minimum halo mass hosting cold dense gas for different streaming velocities, given at their starting redshift $z=200$, from \citet{Schauer19} are shown as horizontal black lines.}
    \label{fig:compare_JLW_mass}
\end{figure}
